%-------------------------------------------
% Resume in LaTeX
% Original Author : Sourabh Bajaj
% License : MIT
% Modified By: Kandarp Khandwala
%-------------------------------------------

\documentclass[a4paper,10pt]{article}

% Set the text height and width and the margins such that the page is almost full. 
\usepackage[empty]{fullpage}
% Set the default font
\usepackage{tgpagella}

\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
% Pretty bulleting
\usepackage{verbatim}
\usepackage{enumitem}

% Some standard packages
\usepackage[hidelinks,pdfauthor={Kandarp Khandwala},pdftitle={Kandarp_Khandwala_Resume}]{hyperref}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{2.5in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-11pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


%-------------------------
% Custom commands

%%%%%%%% TODO %%%%%%%%
% Clean up custom commands %
%%%%%%%%%%%%%%%%%%%%

\newcommand{\resumeItem}[2]{
  \vspace{-0.5pt} \item\small{
    \textbf{#1}{: #2}
  }
}

\newcommand{\projectItem}[1]{
  \item\small{#1}}


\newcommand{\resumeSubheadingOld}[4]{
	\vspace{1pt}
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \large{\textbf{#1}} & \textit{\small #4} \\
      \textit{\small#2} & \textit{\small#3} \\
    \end{tabular*}
}

\newcommand{\resumeSubheading}[3]{
	\item
	\textbf{#2} \textbar{} \textbf{#1} \hfill \textit{#3}
}

\newcommand{\projectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \large{\textbf{#1}} & \textit{\small #2} \\
    \end{tabular*}\vspace{-1.5pt}
}


\newcommand{\resumeSubItem}[2]{
	\vspace{2pt}\item
	\textbf{#1}: {#2}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]\setlength\itemsep{0pt}\setlength{\parskip}{-1pt}\setlength{\parsep}{0pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\vspace{-1pt}\begin{itemize}[leftmargin=*]\setlength\itemsep{.5pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}}


%-------------------------------------------
\begin{document}

\centerline{\LARGE{Kandarp Khandwala}}
\centerline{\normalsize{Baltimore, MD \textbar{} \href{mailto:kandarp.k@jhu.edu}{kandarp.k@jhu.edu} \textbar{} +1 (443) 763-9251 \textbar{} \href{https://github.com/kandarpck}{Github: kandarpck} }}
\centerline{\normalsize{\href{http://kandarpck.appspot.com/}{Website: kandarpck.appspot.com}  \textbar{} \href{https://www.linkedin.com/in/kandarpkhandwala}{LinkedIn: linkedin.com/in/kandarpkhandwala}}}

%\centerline{\Large{Jane Doe}}
%\centerline{\normalsize{\href{mailto:jane@gmail.com}{jane@gmail.com} \textbar{} +91122454747 \textbar{} \href{http://jane.appspot.com/}{jane.appspot.com} \textbar{} \href{https://github.com/jane}{Github: jane} \textbar{} \href{https://www.linkedin.com/in/jane}{LinkedIn: jane}}}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheadingOld
  {Masters in Computer Science \& Security \textbar{} Johns Hopkins University}
  {Courses: Natural Language Processing, Advanced Cryptographic Systems, Blockchains and Cryptocurrencies.}{Aug. 17 - Dec 18 (expected)}{GPA: 3.81}
    \resumeSubheadingOld
      {Bachelors in Computer Engineering \textbar{} Mumbai University}
      {Courses: Algorithms, Operating Systems, Data Mining, Advanced Computer Networks, Artificial Intelligence.}{Jul. 11 - May. 15}{GPA: 3.61}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
      \projectHeading{Software Engineering Intern \textbar{} Verizon}
 	 {May. 18 - Aug. 18}
  	\resumeItemListStart
  		\resumeItem{Drive Cleaner}
  			{Developed the API Backend Microservice to calculate a score based on driving habits and car conditions. Provided tips to improve the score which helped the user in fuel and environmental savings.}
  \resumeItemListEnd
  
  \projectHeading
	  {Research Assistant \textbar{} Institute of Data Intensive Engineering and Science %\textbar{} \textit{\small \href{http://idies.jhu.edu}{idies.jhu.edu}}}\
	}{Aug. 17 - May. 18}
  	\resumeItemListStart
  		\resumeItem{Deep Learning}
  			{Analyzed raw galaxy images, identified and accurately predicted the type of galaxy observed. Generated a realistic simulated universe and performed predictive analysis on the simulated data.}
  \resumeItemListEnd
  
  
    \projectHeading
      {Software Engineer \textbar{} JPMorgan Chase Co. \textbar{} \textit{\small Credit Risk and Profit and Loss(PnL)}}
     {Jul. 15 - Jun. 17}
      \resumeItemListStart
%         \resumeItem{Batch Split}
%          {Improved resiliency and performance of the End of Day(EOD) Fixed Income risk batch which reduced Priority 1 issues by 33\% and improved overall timing by one hour.}
        \resumeItem{DevOps}
        {Lead the DevOps initiative in the team by bringing the support team up to speed using knowledge transfer sessions. \\
        Identified pain points and built a dashboard tool unifying applications which increased productivity by 20\%}
        \resumeItem{Secured Lending}
          {Interacted with traders and orchestrated the development of a comprehensive suite of five applications for high-value Lending and Collateral transactions, shortening the turnaround time from days to minutes.}
      \resumeItemListEnd
      
   
    \projectHeading{Summer Intern \textbar{} Avocation Education Services Pvt. Ltd.}
   {May. 15 - Jul. 15}
   \resumeItemListStart
   		\resumeItem{Security and Optimization}
%   		{Reduced the web application downtime by 50\% by optimizing the code and streamlining the infrastructure leading to a sustained 3x increase in web traffic over the year.}
%   		\resumeItem{Server Hardening}
   		{Enhanced Web Security by adding API authentication, HTTPS, closing down on unrestricted ports, adding measures to protect against DDoS attacks and implementing Identity \& Access Management.}
   \resumeItemListEnd
%   

%-----------Extra Experience-----------------
%    \projectHeading{Summer Intern \textbar{} Gray Routes}
% 	{Jun. 14 - Aug 14}
% 	\resumeItemListStart
% 	\resumeItem{Intelligent Systems}
% 	{Conceptualized innovative solutions for last-mile delivery and logistics by combining Location Services and Machine %	 Learning for efficient inventory management and optimized route prediction.}
% 	\resumeItemListEnd
      
%     \resumeSubheading
%      {Stupidsid}
%      {Developer Intern}{Summer 13 and 15}
%     \resumeItemListStart
%        \resumeItem{Application Scaling}
%          {Revamped the back-end application architecture and API services, leading to a sustained 3x increase in web traffic over the year while also slashing costs to half.}
%       \resumeItem{Mobile First}
%          {Pioneered the design and development of Android applications which empowered the startup to adopt a distinguished strategy and triumph over the competition.}
%      \resumeItemListEnd
 
%------------------------------------------------
    
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\small{\item{
		{Python, Pandas, Django, \hfill{} Java, Spring, Android, Go, Unix, \hfill{} TensorFlow, Snort, \hfill{} AWS, GCP, \hfill{} Solr, \hfill{} Git, PostgreSQL, \LaTeX}
		
}}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects and Publications}
  \resumeSubHeadingListStart
    
    
    \projectHeading{Decentralized Public Key Infrastructure using Ethereum Smart Contracts}{Jan. 18 - May. 18} 
    \resumeItemListStart
    \projectItem{Developed a PKI with built-in certificate transparency to make it easy to detect rogue certificates for fine-grained identity management and trust.}
    \resumeItemListEnd
    
    \projectHeading{Mini Projects}{Sep. 17 - May. 18} 
    \resumeItemListStart
    	\projectItem{Simulate an attack on Bitcoin by developing a Miner with 51\% hash power to maximize profits.}
    	\projectItem{Cryptographic Protocol Analysis of the Telegram encryption protocols.}
    	\projectItem{Implemented the Vigenere, AES, RSA and Rabin Cryptosystems and launched Timing \& Padding Oracle attacks against them.}
	    \projectItem{Thorough Analysis, Reporting of the top 10 OWASP vulnerabilities and demonstrating attacks and defenses against them.}
    \resumeItemListEnd
    
   \projectHeading{Personalized Search Engine and Mobile Assistant}{Aug. 14 - Mar. 15} 
    \resumeItemListStart
      \projectItem{Programmed a small-scale search engine by extending Apache Solr, delivering high quality, efficient search results and context aware customized information based on the user's current likes and likelihood of future preferences.}
     \resumeItemListEnd
   
   \projectHeading{Dynamic Context Aware Traffic System Optimization}{Jan. 14 - May. 14} 
    \resumeItemListStart
      \projectItem{Proposed algorithmic changes after statistical analyses on vehicular traffic data leading to 15\% traffic efficiency improvement.}
      \projectItem{Nominated as the best departmental project. Picked among top ten ideas from 600 national entries at 'All India Science and Engineering' Contest organized by KPIT.}
      \projectItem{The findings for this research were published in IJERT. arXiv:1407.5212 (2014). doi: 10.5120/17586-8253 Aug. 14}
     \resumeItemListEnd

   \projectHeading{Road Bump Data Analysis using Automated Real Time Data Stream to Big Query}{Jun. 14 - Jul. 14} 
    \resumeItemListStart
      \projectItem{Created a data pipeline processor that managed the entire ETL process on Road Bump data collected using mobile sensors delivering an optimized route to transport cheaply.}
     \resumeItemListEnd
   
  \resumeSubHeadingListEnd

%-----HONORS AND AWARDS-------
\section{Honors and Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{Holiday Hack Challenge}
  	  {Reached stage 4/5 of the Network Security yearly challenge.}\hfill \textit{Dec. 16}
    \resumeSubItem{Top Thinker}
      {Award for the 6 most impactful employees among 150 analysts joining JPMorgan.}\hfill \textit{Jul. 15}
    \resumeSubItem{Hackathon - 1st Prize, JPMorgan} 
      {Among 120 competitors selected from 20 colleges.}\hfill \textit{Jul. 14}
    \resumeSubItem{Hackathon - 2nd Prize, Google Developers Group}
      {World Hackathon among 30 participating teams.}\hfill \textit{Oct. 14}
    \resumeSubItem{State Govt. Academic Scholarship}
    {Funding 1 year of education for excellence in the field of Computer Sci.}\hfill \textit{Jun. 11}
  \resumeSubHeadingListEnd

%--------PUBLICATIONS------------
%\section{Publications}
%  \resumeSubHeadingListStart
%    \resumeSubItem{Context Aware Dynamic Traffic Signal Optimization.}
%      {Khandwala K, Sharma R, and Rao S. arXiv:1407.5212 (2014). doi: 10.5120/17586-8253}\hfill \textit{Aug. 14}
%  \resumeSubHeadingListEnd

%--------LEADERSHIP------------
\section{Leadership and Involvement}
  \resumeSubHeadingListStart
    
    \resumeSubheading{JPMorgan Chase \& Co.}{Campus Ambassador}{Oct. 15 - Nov. 16}
    \resumeItemListStart
    \projectItem{Part of the campus recruitment team, interacting with alma mater and ensuring high recruitment standards.}
    \projectItem{Delivered 3 sessions to 500 students for the recruitment drive of 2016.}
    \resumeItemListEnd
    
    \resumeSubheading{JPMorgan Code for Good Hackathon}{Technical Judge and Subject Matter Expert}{Jul. 16 - Jul. 16}
    \resumeItemListStart
    \projectItem{Provided technical expertise as a Subject Matter Expert for Git, Android, and AWS.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Indian Society for Technical Education}{Event Planner and Technical Team}{Jul. 12 - Jul. 14}
    \resumeItemListStart
    \projectItem{Incharge of the Mobile and Web strategy. Built games like Virtual Stock Market Trading which garnered 20000 hits.}
    \resumeItemListEnd
    
	\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}